\section{Considerations and Challenges}

The development of SmartV's cloud infrastructure has forced several key considerations and challenges.

\subsection{Private and Public Cloud}

One critical consideration is the choice between private and public cloud deployment models. While a private cloud offers dedicated resources and enhanced control over security and infrastructure management, there are also much higher initial costs in acquiring the requisite physical infrastructure. By contrast, use of a public cloud provides scalability and cost-efficiency, but reduces the level of control over the underlying infrastructure.

For a web-based and consumer-facing platform such as SmartV, it was decided that ability to easily scale infrastructure to platform usage was a crucial aspect of the transition to cloud infrastructure, and was the primary factor in the choice to use the AWS public cloud.

\subsection{Data Security}

SmartV offers services to a large number of users who understand their data to be both confidentially and securely stored. Implementing secure data storage is extremely important to the web-based platform, and required the use of encryption across S3 and RDS storage to ensure that there are strong barriers between users' data and potential bad actors.

\subsection{Scalability and Elasticity}

As SmartV anticipates a potentially rapid growth in user base and content volume, the ability to scale resources dynamically is a key concern. Ensuring that the cloud infrastructure can efficiently accommodate changes in demand, particularly during peak usage times, is extremely important. Implementing auto-scaling and load balancing strategies, along with the use of AWS services like EC2 and S3, is a vital solution to achieving the desired level of elasticity and scalability.

\subsection{Proof-of-Concept Pricing}

The choice of the AWS public cloud made managing costs during the Proof-of-Concept (POC) phase a critical consideration. Implementing Infrastructure as Code (IaC) allowed us to define, deploy, and manage our cloud resources in a cost-effective manner. By scripting the infrastructure, we could accurately estimate costs, avoid over-provisioning, and utilize AWS's free-tier offerings to our advantage. This also meant we were able to quickly provision and destroy the cloud infrastructure to test our work, requiring very little overhead in the deployment process.
